\section{Conclusions}

\begin{frame}[t]{Summary}
\begin{itemize}
  \item An unified programming model for sequential and parallel modes.
  \item Multiple back-ends available.
  \item Current pattern set:
    \begin{itemize}
      \item \textenum{Data}: \textmark{map}, \textmark{reduce}, \textmark{map/reduce}, \textmark{stencil}.
      \item \textenum{Task}: \textmark{divide/conquer}.
      \item \textenum{Streaming}: \textmark{pipeline} with nesting of \textmark{farm}, \textmark{filter},
            \textmark{reduction}, \textmark{iteration}.
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[t]{Future work}
\begin{itemize}
  \item Integrate additional backends (e.g. FastFlow, CUDA).
  \item Eliminate metaprogramming by using Concepts.
  \item Extend and simplify the interface for data patterns.
  \item Support multi-context patterns.
  \item Better support of NUMA for native back-end. 
  \item More patterns.
  \item More applications.
\end{itemize}
\end{frame}

\begin{frame}[t]{Recent publications}
\begin{scriptsize}
\begin{itemize}
\item
\textgood{A Generic Parallel Pattern Interface for Stream and Data Processing}. 
D. del Rio, M. F. Dolz, J. Fernández, J. D. García. 
Concurrency and Computation: Practice and Experience. 
2017.
\vfill
\item
\textmark{Parallelizing and optimizing LHCb-Kalman for Intel Xeon Phi KNL processors}.
P. Fernandez, D. Rio, M.F. Dolz, J. Fernández, O. Awile, J.D. Garcia,
PDP 2018.
\item
\textmark{Supporting Advanced Patterns in GrPPI: a Generic Parallel Pattern Interface}.
D. R. del Astorga, M. F. Dolz, J. Fernandez, and J. D. Garcia, 
Auto-DaSP 2017 (Euro-Par 2017).
\item
\textmark{Probabilistic-Based Selection of Alternate Implementations for Heterogeneous Platforms}.
J. Fernandez, A. Sanchez, D. del Río, M. F. Dolz, J. D Garcia.
ICA3PP 2017.
2017.
\item
\textmark{A C++ Generic Parallel Pattern Interface for Stream Processing}. 
D. del Río, M. F. Dolz, L. M. Sanchez, J. Garcia-Blas and J. D. Garcia. 
ICA3PP 2016.
\item
\textmark{Finding parallel patterns through static analysis in C++ applications}.
D. R. del Astorga, M. F. Dolz, L. M. Sanchez, J. D. Garcia, M. Danelutto, and M. Torquati, 
International Journal of High Performance Computing Applications, 2017.
\end{itemize}
\end{scriptsize}
\end{frame}

\begin{frame}{GrPPI}
\begin{Large}
\textgood{\url{https://github.com/arcosuc3m/grppi}}
\end{Large}
\end{frame}
